formula1

### 2020-07-20 inst/f1points.Rmd
typo

From figure \r=ef{orderingbypointsandlikelihood}, we see that the
first two drivers (Hamilton, Vettel) are are respectively first and
second according to both ranking ranking procedures; but
R\"{a}ikk\"{o}nen YES I KNOW IT IS WRONG: RMARKDOWN IS DEFECTIVE and
Bottas are third and fourth, and fourth and third, according to points
and likelihood respectively.  The degree of agreement between the two
systems might be quantified as "two", for the positions of the top two
drivers agree.

>>>>

From figure \ref{orderingbypointsandlikelihood}, we see that the
first two drivers (Hamilton, Vettel) are are respectively first and
second according to both ranking ranking procedures; but
R\"{a}ikk\"{o}nen YES I KNOW IT IS WRONG: RMARKDOWN IS DEFECTIVE and
Bottas are third and fourth, and fourth and third, according to points
and likelihood respectively.  The degree of agreement between the two
systems might be quantified as "two", for the positions of the top two
drivers agree.
